Truth space method for caching database queries

### 2015-03-08 english_version/IEEE_conf_sib/paper_main.tex
IEEE siberian conference version was added.

\documentclass[preprint,12pt]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\author{Mosin Sergey, Zykin Sergey}
\usepackage{amssymb,amsmath}
\usepackage{amsthm}
%\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage{xcolor}
%\usepackage{textcomp}
\newtheorem{note}{Note}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\journal{Theoretical Computer Science}

@@

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Truth space method for caching database queries}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{S.~V. Mosin, S.~V. Zykin}

\address{Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences}

\begin{abstract}
We propose a new method of client-side data caching for relational databases
with a central server and distant clients. Data is loaded into client cache
based on queries executed on the central database at the server. These
queries have a special form - "universal relational query". The majority of
search queries to database can be expressed in such form. Besides, this form
allows us to analyze query correctness by checking lossless join property. A
subsequent query may be executed in client's local cache if we can determine
that the query result is entirely contained in the cache. For this we compare
truth spaces of the logical restrictions in new user's query and results of
the queries execution in cache. This method may be used to define lacking data
in cache and execute the query on server for this data only. Problem of data
actualizations in cache is not discussed in this paper. However, it can be
solved by cataloging of queries on server and their serving by triggers in
background mode.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword  keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Relational databases \sep Caching \sep Truth space
\end{keyword}

\end{frontmatter}

@@

\begin{statement}[Inclusion property]
$\forall X \subseteq \<F> \quad M(F) \subseteq M(F[X])$
\label{proj_property_of_inclusion}
\end{statement}
\begin{proof}
If $X = \<F> $, then $F = F[X]$ and $M(F) = M(F[X])$. Assume $X \subset \<F> $.
Consider arbitrary point $a \in M(F)$, i.e. $F(a)=\n{TRUE}$. $F$ to $F[X]$
transformation is made by replacing $T_j$ predicates that contain $A_j \in
\<F> $ attribute, such that $A_j \notin X$ with $\n{TRUE}$ value. We get
$F([X])=\n{TRUE}$ according to (\ref{def_F_1}) and (\ref{def_F_2}). Therefore,
$a \in M(F[X])$.
\end{proof}

@@

\begin{statement}
Assume $\Re_1 = R_1 \Join \dots \Join R_k$ - natural join of some $k$ relations.
Also assume $\Re_2 = R_1 \Join \dots \Join R_k \Join R_{k+1} \Join \dots \Join
R_{n}$. Then $\Re_2 [\langle \Join_{i=1}^{k} R_i \rangle] \subseteq \Re_1$
\label{join_property}
\end{statement}
\begin{proof}
It is so indeed, because joining additional relations to $\Re_1$ can only
remove some tuples that were presented there. After the projection, we will get
the same relation $\Re_1$ if no tuples were deleted or some subset otherwise. The
order of joins doesn't matter because of commutativity of this operation.
\end{proof}

@@

\bibliographystyle{elsarticle-num}
\bibliography{references}

>>>>

\documentclass{article}

@@

%% The amssymb package provides various useful mathematical symbols
\author{Mosin Sergey, Zykin Sergey}
\title{Truth space method for caching database queries}

\usepackage{amssymb,amsmath}
\usepackage{amsthm}

\newtheorem{note}{Note}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

@@

\maketitle

Adress: Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences

\begin{abstract}
We propose a new method of client-side data caching for relational databases
with a central server and distant clients. Data is loaded into client cache
based on queries executed on the central database at the server. These
queries have a special form - "universal relational query". The majority of
search queries to database can be expressed in such form. Besides, this form
allows us to analyze query correctness by checking lossless join property. A
subsequent query may be executed in client's local cache if we can determine
that the query result is entirely contained in the cache. For this we compare
truth spaces of the logical restrictions in new user's query and results of
the queries execution in cache. This method may be used to define lacking data
in cache and execute the query on server for this data only. Problem of data
actualizations in cache is not discussed in this paper. However, it can be
solved by cataloging of queries on server and their serving by triggers in
background mode.

Keywords: Relational databases, Caching, Truth space
\end{abstract}

@@

\begin{statement}[Inclusion property]
$\forall X \subseteq \<F> \quad M(F) \subseteq M(F[X])$
\label{proj_property_of_inclusion}
\end{statement}

@@

\begin{statement}
Assume $\Re_1 = R_1 \Join \dots \Join R_k$ - natural join of some $k$ relations.
Also assume $\Re_2 = R_1 \Join \dots \Join R_k \Join R_{k+1} \Join \dots \Join
R_{n}$. Then $\Re_2 [\langle \Join_{i=1}^{k} R_i \rangle] \subseteq \Re_1$
\label{join_property}
\end{statement}

@@

\begin{thebibliography}{1}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{zyk_pol}
S.~Zykin, A.~Poluyanov, Multidimensional data building using intermediate
  representations., Administration problems~(5) (2013) 54--59.

\bibitem{chang}
C.-S. Park, M.-H. Kim, Y.-J. Lee, Usability-based caching of query results in
  olap systems., Journal of Systems and Software 68~(2) (2003) 103--119.

\bibitem{baralis}
E.~Baralis, S.~Paraboschi, E.~Teniente,
  \href{http://dl.acm.org/citation.cfm?id=645923.671019}{Materialized views
  selection in a multidimensional database}, in: Proceedings of the 23rd
  International Conference on Very Large Data Bases, VLDB '97, Morgan Kaufmann
  Publishers Inc., San Francisco, CA, USA, 1997, pp. 156--165.
\newline\urlprefix\url{http://dl.acm.org/citation.cfm?id=645923.671019}

\bibitem{kalnis}
P.~Kalnis, D.~Papadias, Proxy-server architectures for olap., in: S.~Mehrotra,
  T.~K. Sellis (Eds.), SIGMOD Conference, ACM, 2001, pp. 367--378.

\bibitem{Afrati06}
F.~N. Afrati, C.~Li, P.~Mitra, Rewriting queries using views in the presence of
  arithmetic comparisons., Theor. Comput. Sci. 368~(1-2) (2006) 88--123.

\bibitem{Keller96}
A.~M. Keller, J.~Basu, A predicate-based caching scheme for client-server
  database architectures, VLDB J. 5~(1) (1996) 35--47.

\bibitem{shim}
J.~Shim, P.~Scheuermann, R.~Vingralek, Dynamic caching of query results for
  decision support systems., in: SSDBM, 1999, pp. 254--263.

\end{thebibliography}
